### 2019-03-19 papers.tex
Pull in an exasperated new paper
papers.tex: Another exasperated keyword
Pull in Stefan's review of paper 19
papers.tex: Remove pesky brackets that weren't typesetting correctly

\addtrack
	{}{Machine learning}
\addpaper
	{Color- and piece-blind chess}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, handicaps, man-in-the-middle attacks, neural networks}
	{SIGBOVIK_2019_paper_36}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/chess/blind}}
\addpaper
	{Dimensionality-reducing encoding for classification of Pythagorean engendered numbers}
	{Rany Tith and Oscar I.\@ Hernandez}
	{Keywords: number theory, machine learning, encoding, information theory, classification, gender theory, integers, globalization, computation, mathematics}
	{SIGBOVIK_2019_paper_28}
	{0cm}
	{}
\addpaper
	{emojizip: A text compression system based on pictogram-kiloword equivalence}
	{William Gunther and Brian Kell}
	{Keywords: data compression, TensorFlow, [laughing crying emoji]}
	{SIGBOVIK_2019_paper_39}
	{0cm}
	{\link[The authors assure us the materials will be available ``if they get around to it'':]{http://zifyoip.com/emojizip}}
\addreview{SIGBOVIK_2019_review_39}{0cm}
\addpaper
	{Meta-meta-learning for neural architecture search through arXiv Descent}
	{Antreas Antoniou \textit{et al.}}
	{Keywords: meta, meta-meta, deep, NAS}
	{SIGBOVIK_2019_paper_11}
	{0cm}
	{}
\addpaper
	{Towards automatic low hanging fruit identification for the steering of ML research}
	{Nick Frosst and Aidan Gomez}
	{Keywords: machine learning, detection, segmentation, orientation, apple, akee, apricot, avocado, banana, bilberry, blackberry, blackcurrant, black sapote, blueberry, boysenberry, Buddha's hand (fingered citron), crab apples, currant, cherry, cherimoya (custard apple), chico fruit, cloudberry, coconut, cranberry, cucumber, damson, date, dragonfruit (or pitaya), durian, elderberry, feijoa, fig, goji berry, gooseberry, grape, raisin, grapefruit, guava, honeyberry, huckleberry, jabuticaba, jackfruit, jambul, japanese plum, jostaberry, jujube, juniper berry, kiwano (horned melon), kiwifruit, kumquat, lemon, lime, loquat, longan, lychee, mango, mangosteen, marionberry, melon, cantaloupe, honeydew, watermelon, miracle fruit, mulberry, nectarine, nance, olive, orange, blood orange, clementine, mandarine, tangerine, papaya}
	{SIGBOVIK_2019_paper_32}
	{0cm}
	{}

@@

\addtrack
	{}{Chess}
\addpaper
	{Is ``Dicong Qiu. Is this the shortest SIGBOVIK paper? From 2018 SIGBOVIK paper'' the shortest SIGBOVIK paper?}
	{Thomas Bach}
	{Keywords: o, o, o}
	{SIGBOVIK_2019_paper_14}
	{0cm}
	{}
\addpaper
	{Is this the tiniest SIGBOVIK paper ever?}
	{Mitchell Jones}
	{Keywords: tiny, zoom, Fermat}
	{SIGBOVIK_2019_paper_5}
	{0cm}
	{}
\addpaper
	{No, this is the tiniest SIGBOVIK paper ever.}
	{Patrick Lin}
	{Keywords: tony, zoom, Mitchell, heart}
	{SIGBOVIK_2019_paper_6}
	{0cm}
	{}
\addpaper
	{Revisiting the shortest SIGBOVIK paper / The revised shortest SIGBOVIK paper}
	{Richard Wardin}
	{Keywords: word golf, revisioned paper, deflation}
	{SIGBOVIK_2019_paper_9}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_9}{0cm}

@@

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addpaper
	{93\% of paint splatters are valid Perl programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{\vspace{0.15in} {\scriptsize The authors assure us the materials will be available ``soon'' from: \url{http://famicol.in/sigbovik}} \raisebox{0in}{\includegraphics[height=0.75in]{participation}}}
\addpaper
	{A survey and projection of SIGBOVIK trends}
	{Jenny H. Lin}
	{Keywords: SIGBOVIK, self referential, ``Figures'', join the committee}
	{SIGBOVIK_2019_paper_chair}
	{0cm}
	{}

>>>>

\addtrack
	{}{Machine learning}
\addpaper
	{Color- and piece-blind chess}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: chess, handicaps, man-in-the-middle attacks, neural networks}
	{SIGBOVIK_2019_paper_36}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/chess/blind}}
\addpaper
	{Dimensionality-reducing encoding for classification of Pythagorean engendered numbers}
	{Rany Tith and Oscar I.\@ Hernandez}
	{Keywords: number theory, machine learning, encoding, information theory, classification, gender theory, integers, globalization, computation, mathematics}
	{SIGBOVIK_2019_paper_28}
	{0cm}
	{}
\addpaper
	{emojizip: A text compression system based on pictogram-kiloword equivalence}
	{William Gunther and Brian Kell}
	{Keywords: data compression, TensorFlow, laughing crying emoji}
	{SIGBOVIK_2019_paper_39}
	{0cm}
	{\link[The authors assure us the materials will be available ``if they get around to it'':]{http://zifyoip.com/emojizip}}
\addreview{SIGBOVIK_2019_review_39}{0cm}
\addpaper
	{Meta-meta-learning for neural architecture search through arXiv Descent}
	{Antreas Antoniou \textit{et al.}}
	{Keywords: meta, meta-meta, deep, NAS}
	{SIGBOVIK_2019_paper_11}
	{0cm}
	{}
\addpaper
	{Towards automatic low hanging fruit identification for the steering of ML research}
	{Nick Frosst and Aidan Gomez}
	{Keywords: machine learning, detection, segmentation, orientation, apple, akee, apricot, avocado, banana, bilberry, blackberry, blackcurrant, black sapote, blueberry, boysenberry, Buddha's hand (fingered citron), crab apples, currant, cherry, cherimoya (custard apple), chico fruit, cloudberry, coconut, cranberry, cucumber, damson, date, dragonfruit (or pitaya), durian, elderberry, feijoa, fig, goji berry, gooseberry, grape, raisin, grapefruit, guava, honeyberry, huckleberry, jabuticaba, jackfruit, jambul, japanese plum, jostaberry, jujube, juniper berry, kiwano (horned melon), kiwifruit, kumquat, lemon, lime, loquat, longan, lychee, mango, mangosteen, marionberry, melon, cantaloupe, honeydew, watermelon, miracle fruit, mulberry, nectarine, nance, olive, orange, blood orange, clementine, mandarine, tangerine, papaya}
	{SIGBOVIK_2019_paper_32}
	{0cm}
	{}

@@

\addtrack
	{}{Chess}
\addpaper
	{Is ``Dicong Qiu. Is this the shortest SIGBOVIK paper? From 2018 SIGBOVIK paper'' the shortest SIGBOVIK paper?}
	{Thomas Bach}
	{Keywords: o, o, o}
	{SIGBOVIK_2019_paper_14}
	{0cm}
	{}
\addpaper
	{Is this the tiniest SIGBOVIK paper ever?}
	{Mitchell Jones}
	{Keywords: tiny, zoom, Fermat}
	{SIGBOVIK_2019_paper_5}
	{0cm}
	{}
\addpaper
	{No, this is the tiniest SIGBOVIK paper ever.}
	{Patrick Lin}
	{Keywords: tony, zoom, Mitchell, heart}
	{SIGBOVIK_2019_paper_6}
	{0cm}
	{}
\addpaper
	{Revisiting the shortest SIGBOVIK paper / The revised shortest SIGBOVIK paper}
	{Richard Wardin}
	{Keywords: word golf, revisioned paper, deflation}
	{SIGBOVIK_2019_paper_9}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_9}{0cm}
\addpaper
	{On the shortness of SIGBOVIK papers}
	{An exasperated reviewer}
	{Keywords: bad jokes too thoroughly explored, mean girls, paper length, battery of deceased equine organisms}
	{SIGBOVIK_2019_paper_shortest}
	{0cm}
	{}

@@

\addtrack
	{}{Measurement studies}
\addpaper
	{Applications of Standard ML at Google}
	{Andrew Benson}
	{Keywords: SML, Standard ML, one-fifty, Harper, Google, software engineering, programming languages}
	{SIGBOVIK_2019_paper_19}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_19}{0cm}
\addpaper
	{93\% of paint splatters are valid Perl programs}
	{Colin McMillen and Tim Toady}
	{Keywords: perl, OCR, regret}
	{SIGBOVIK_2019_paper_34}
	{0cm}
	{\vspace{0.15in} {\scriptsize The authors assure us the materials will be available ``soon'' from: \url{http://famicol.in/sigbovik}} \raisebox{0in}{\includegraphics[height=0.75in]{participation}}}
\addpaper
	{A survey and projection of SIGBOVIK trends}
	{Jenny H. Lin}
	{Keywords: SIGBOVIK, self referential, ``Figures'', join the committee}
	{SIGBOVIK_2019_paper_chair}
	{0cm}
	{}
